A Proposed Translation of B Implementations to the LLVM

### 2013-07-20 PAPERS/2013-SBMF/paper_short.tex
almost there

\begin{abstract}
  The aim of this work is to lay the foundations of a multi-platform code
  generator for the B method. In particular, this paper presents a translation
  procedure from a large subset of the B language for implementations towards
  LLVM source code. This translation is defined formally as a set of rules
  defined recursively on the abstract syntax for B implementations. It handles
  the following elements of the B language: simple data types, imperative
  instructions and component compositions. 
\end{abstract}

@@

\paragraph{Overview.} Following this introduction, the paper is organized as
follows. The implementation constructs of the B language, and selected elements
of the LLVM are presented in section~\ref{sec:b-impl}
and~\ref{sec:llvm}. Section~\ref{sec:overview} presents a bird's-eye view that
is then detailed in sections~\ref{sec:module} (for component modularity)
~\ref{sec:data} (for data aspects),~\ref{sec:expr} (expressions) and
instructions~\ref{sec:control}. We conclude and discuss future work
in~\ref{sec:conclusion}.

@@

Figure~\ref{tab:node-attr} summarizes the structure
of the abstract syntax that is relevant in the definition of the proposed
translation and introduces identifiers used in the definition of the
translation. For instance, and for the purpose of the translation, the relevant
components of a B implementation are: \B{id}, the name identifying the
implementation within the project; \B{see}, a set of references to other modules
containing definitions used in the implementation; \B{const}, a set of constant
names, their type and their values; \B{imp}, a sequence of optionally
prefixed B machines corresponding to external modules instantiated in the
implementation; \B{var}, a set of variable names, their type and possibly
additional functional restrictions forming the rest of the state; \B{init}, a
sequence of instructions executed upon initialization of the implementation;
\B{op}, a set of operations, each being an algorithmic description of the
different functionalities provided by the implementation.

@@

Note that the translation presented in this paper only considers types \B{INT}
(integer) and \B{BOOL} (Boolean). Accordingly, the expression language consists
in arithmetic operations \B{-} (unary and binary), \B{+}, \B{*}, \B{/}, \B{mod},
% \B{**} (exponentiation), 
\B{succ} and \B{pred} and Boolean operations
\B{$\land$}, \B{$\lor$}, \B{$\neg$} as well as relations \B{=}, \B{$\neq$},
\B{$>$}, \B{$<$}, \B{$\leq$} and \B{$\neq$}. Atomic expressions are identifiers,
Boolean constants \B{FALSE} and \B{TRUE}, integer literals, and integer
constants \B{MAXINT} and \B{MININT}. The development through the application of
the B method ensures the absence of overflows and underflows.
%TODO optionally to remove unsed elements in this table

@@

        \B{imp} & : & seq \B{Impo} \\

@@

        \multicolumn{3}{|c|}{Imported machine: \B{Impo}} \\

@@

        \B{scope} & : & \B{Impl} \alt \B{Oper}

@@

      respectively}

>>>>

\begin{abstract}
The aim of this work is to lay the foundations of a multi-platform code
generator for the B method. In particular, this paper presents a proposed
translation  procedure from a subset of the B language for implementations
towards LLVM source code. This translation is defined formally as a set of
rules defined recursively on the abstract syntax for B implementations. It 
presents a overview of translation and a simplified example.
\end{abstract}

@@

\paragraph{Overview.} Following this introduction, the paper is organized as
follows. The implementation constructs of the B language, and selected elements
of the LLVM are presented in section~\ref{sec:b-impl} and~\ref{sec:llvm}.
Section~\ref{sec:control} presents the main rules to translate the operations and
instructions. We conclude and discuss future work in~\ref{sec:conclusion}.

@@

Figure~\ref{tab:node-attr} summarizes the structure
of the abstract syntax that is relevant in the definition of the proposed
translation and introduces identifiers used in the definition of the
translation. For instance, and for the purpose of the translation, the relevant
components of a B implementation are: \B{id}, the name identifying the
implementation within the project; \B{see}, a set of references to other modules
containing definitions used in the implementation; \B{const}, a set of constant
names, their type and their values; \B{imp},%a sequence of optionally prefixed
%B machines corresponding to external modules instantiated in the
%implementation;
\B{var}, a set of variable names, their type and possibly
additional functional restrictions forming the rest of the state; \B{init}, a
sequence of instructions executed upon initialization of the implementation;
\B{op}, a set of operations, each being an algorithmic description of the
different functionalities provided by the implementation.

@@

Note that the translation presented in this paper only considers types \B{INT}
(integer) and \B{BOOL} (Boolean). Accordingly, the expression language consists
in arithmetic operations \B{-} (unary and binary), \B{+}, \B{*}, \B{/}, \B{mod},
\B{succ} and \B{pred} and Boolean operations
\B{$\land$}, \B{$\lor$}, \B{$\neg$} as well as relations \B{=}, \B{$\neq$},
\B{$>$}, \B{$<$}, \B{$\leq$} and \B{$\neq$}. Atomic expressions are identifiers,
Boolean constants \B{FALSE} and \B{TRUE}, integer literals, and integer
constants \B{MAXINT} and \B{MININT}. The development through the application of
the B method ensures the absence of overflows and underflows.

@@

%        \B{imp} & : & seq \B{Impo} \\

@@

        %\multicolumn{3}{|c|}{Imported machine: \B{Impo}} \\
        %\hline
        %\B{id} & : & \B{Name} \\
        %\B{pre} & : & opt \B{Name} \\
        %\hline

@@

        \B{scope} & : & \B{Impl} \alt \B{Oper}\\

@@

      respectively.}
